Interval Probability for Fuzzy Quantum Theories

### 2016-05-07 prob.tex
comments

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$.\\
\yutsung{
May I confirm how many times needle cross the line within $3408$ needles?
Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
close to $0.6366197193098592$ enough\ldots }\\
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.

@@

>>>>

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$.\\
\yutsung{
May I confirm how many times needle cross the line within $3408$ needles?
Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
close to $0.6366197193098592$ enough\ldots }\\
\amr{
There are several articles and papers on the experiment. I got these
values from wikipedia and mathworld. We need to get precise references
and cite the papers describing the experiments. The actual values
don't matter though.
}
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.

@@

\amr{
The idea will be the following. First describe quantum probability
spaces conventionally. Then talk about the following:
\begin{itemize}
\item the dimension of the Hilbert space is a parameter that is like
  the number of needles; it gives an upper bound on the accuracy of
  the numbers that are relevant in expressing probabilities
\item the intervals will come from two things: the fact that states
  can only be prepared to a certain accuracy so when we say the state
  is $\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$
\item similarly when we do an experiment with $\proj{\phi}$ we are
  really testing a family of projections that are near $\proj{\phi}$;
  this fuziness will cause the probability to only be specifiable as intervals
\end{itemize}
}
